Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-21 prop_letter.tex
prop_letter.tex Updating Kochen-Specker interpertation...

\begin{condition}\label{cond:one-one}If a set of commuting projectors~$P_{i}$
satisfies $\sum_{i}P_{i}=1$, then there exists exactly one $P_{i_{0}}$
such that $v\left(P_{i_{0}}\right)=1$ and $v\left(P_{i}\right)=0$
for $i\ne i_{0}$.\end{condition}

@@

\noindent \begin{condition}\label{cond:one-one-0-deterministicQIVPM}For
a $0$-deterministic QIVPMs~$\bar{\mu}$, if a set of commuting projectors~$P_{i}$
satisfies $\sum_{i}P_{i}=1$, then there exists exactly one $P_{i_{0}}$
such that $\bar{\mu}\left(P_{i_{0}}\right)=\necess$ and $\bar{\mu}\left(P_{i}\right)=\imposs$
for $i\ne i_{0}$.\end{condition}

@@

\begin{condition}\label{cond:eigenvalue-0-deterministicQIVPM}For
a $0$-deterministic QIVPMs~$\bar{\mu}$, $\expval{\mathbf{O}}_{\bar{\mu}}$
must be an eigenvalue of $\mathbf{O}$.\end{condition}

\begin{condition}\label{assu:times-0-deterministicQIVPM}For a $0$-deterministic
QIVPMs~$\bar{\mu}$, if $\mathbf{O}_{0}$ and $\mathbf{O}_{1}$ are
commuting, then $\expval{\mathbf{O}_{0}\mathbf{O}_{1}}_{\bar{\mu}}=\expval{\mathbf{O}_{0}}_{\bar{\mu}}\expval{\mathbf{O}_{1}}_{\bar{\mu}}$.\end{condition}

@@

\begin{assumption}\label{assu:delta-deterministicQIVPM}There exists
a $\delta$-deterministic QIVPM.\end{assumption}

@@

\noindent I personally believe they are approximately hold for small
$\delta$, but void when $\delta$ is large enough.

I think these two properties might be weakened when $0<\delta<\frac{1}{3}$,
and completely break down when $\delta\ge\frac{1}{3}$. (Need a proof!)
If this is the case, the correct statement is that ``the assumption
of non-contextuality hidden variable theory could be considered hold
when $\delta<\frac{1}{3}$, and is completely void when $\delta\ge\frac{1}{3}$.''
So we should not even ask ``whether the existence of QIVPMs when
$\delta\ge\frac{1}{3}$ implies non-contextuality hidden variable
theory or not.'' A little bit different analog could be: we should
not ask ``where is the momentum of a particle when we measure its
position...''

>>>>

\begin{condition}\label{cond:one-one}Given an orthonormal basis~$\Omega$,
then there exists exactly one $\ket{\psi_{i_{0}}}\in\Omega$ such
that $v\left(\proj{\psi_{i_{0}}}\right)=1$ and $v\left(\proj{\psi_{i}}\right)=0$
for $i\ne i_{0}$.\end{condition}

@@

\begin{condition}[0-deterministic Variant of Condition~\ref{cond:one-one}]\label{cond:one-one-0-deterministicQIVPM}For
a $0$-deterministic QIVPMs~$\bar{\mu}$, given an orthonormal basis~$\Omega$,
then there exists exactly one $\ket{\psi_{i_{0}}}\in\Omega$ such
that $\bar{\mu}\left(\proj{\psi_{i_{0}}}\right)=\necess$ and $\bar{\mu}\left(\proj{\psi_{i}}\right)=\imposs$
for $i\ne i_{0}$.\end{condition}

@@

\begin{condition}[0-deterministic Variant of Condition~\ref{cond:eigenvalue}]\label{cond:eigenvalue-0-deterministicQIVPM}For
a $0$-deterministic QIVPMs~$\bar{\mu}$, $\expval{\mathbf{O}}_{\bar{\mu}}$
must be an eigenvalue of $\mathbf{O}$.\end{condition}

\begin{condition}[0-deterministic Variant of Assumption~\ref{assu:times}]\label{assu:times-0-deterministicQIVPM}For
a $0$-deterministic QIVPMs~$\bar{\mu}$, if $\mathbf{O}_{0}$ and
$\mathbf{O}_{1}$ are commuting, then $\expval{\mathbf{O}_{0}\mathbf{O}_{1}}_{\bar{\mu}}=\expval{\mathbf{O}_{0}}_{\bar{\mu}}\expval{\mathbf{O}_{1}}_{\bar{\mu}}$.\end{condition}

@@

\begin{assumption}[Finite-precision Extension of {Condition~}\ref{cond:sum-one}]\label{assu:delta-deterministicQIVPM}There
exists a $\delta$-deterministic QIVPM.\end{assumption}

@@
